---
title: "Output losses for financial crisis: a comparison with the literature"
output: html_notebook
---


```{r echo = F}
# Set periods IRFs
periods = seq(1:5)


```


# Dataframe for estimation:
```{r echo = F}

# Compose dataframe for estimations:

# Let's normalize the indexes we are interested in:

indexes_2normalize <- c("Currency_crisis_severe","Soft_recession","Severe_recession")


annual_tf_idf_norm <- annual_tf_idf %>% 
  ungroup () %>%
  mutate_at(vars(indexes_2normalize), funs(norm = (. - mean(.,na.rm=T))/sd(.,na.rm=T))) 

# Download World Bank data:

growth_df <- wb(country = "countries_only",indicator = "NY.GDP.MKTP.KD",startdate = 1954, enddate = 2016) %>% 
  rename(ISO3_Code = iso3c, 
         year = date,
         gdp_growth = value) %>% 
  select(ISO3_Code, year, gdp_growth)

# Use country group classification:

classification <- import("../Betin_Collodel/2. Text mining IMF_data/datasets/comparison/other_data.RData") %>% 
  select(ISO3_Code,Income_group,group) %>% 
  filter(!duplicated(ISO3_Code))


# Merge final df:

lp_df <- merge(annual_tf_idf_norm,
               growth_df,
               by = c("ISO3_Code","year")) %>% 
  merge(classification, by=c("ISO3_Code"), all.x = TRUE) %>% 
  select(ISO3_Code, year, Currency_crisis_severe_norm, gdp_growth, Income_group, group)

# Check:

head(lp_df)


```

# Estimation:
\begin{align}
y_{i,t+h} - y_{i,t} = \alpha_i + \Lambda CC_{i,t} + y_{t-1} + e_{i,t+h}
\end{align}

with h= 1,...,5 and $y_{t+h} - y_{t}$ the cumulative change from time $t$ to $t + h$ in 100 times the log of real GDP, $CC_{i,t}$ dummy for currency crisis and lagged output $y_{i,t-1}$ to control for country specific trends in output pre-crisis.

# Local proj. with RR index:
```{r echo = F}

# Create a function with argument the country group we want to analyze:

local_proj_rr <- function(country_group){

rr_local <- rr %>% merge(growth_df) %>% merge(classification)

if(country_group != "complete"){
  rr_local <- rr_local %>% filter(group == country_group)
}

list_jorda_rr <- periods %>%
  map(~ rr_local %>% mutate(gdp_growth = log(gdp_growth)) %>% group_by(ISO3_Code) %>% mutate(lag_gdp = dplyr::lag(gdp_growth,1)) %>% mutate(gdp_growth = dplyr::lead(gdp_growth,.x) - gdp_growth)) %>%
  map(~ .x %>% mutate(CC.RR = dplyr::lead(CC.RR,1))) %>% 
  map(~ .x %>% ungroup())

results_jorda_rr <- list_jorda_rr %>% 
  map(~ plm(gdp_growth ~ CC.RR + lag_gdp, .x, effect = "individual",model = "within")) %>% 
  map(~ data.frame(coef_rr = .x[["coefficients"]]*100, ci = confint(.x)*100)) %>% 
  map(~ .x %>% slice(1)) %>% 
  bind_rows() %>% 
  cbind(periods) %>% 
  rename(lower_rr = ci.2.5.., 
         upper_rr = ci.97.5..)

plot_jorda_rr <- results_jorda_rr %>% 
  ggplot(aes(periods, coef_rr)) +
  geom_line(col = "blue") +
  geom_line(aes(y = lower_rr), linetype = "dashed", col = "white") +
  geom_line(aes(y = upper_rr), linetype = "dashed", col = "white") +
  geom_ribbon(aes(ymin = lower_rr, ymax = upper_rr),alpha = 0.2) +
  theme_bw() 

list(df_results = results_jorda_rr, plot = plot_jorda_rr)

}

local_proj_rr("complete")[["plot"]]



```


# Local proj. with our dummy:
```{r echo=F}

local_proj_dummy <- function(country_group){

if(country_group != "complete"){
  lp_df <- lp_df %>% filter(group == country_group)
}
  
  
list_jorda_df <- periods %>%
  map(~ lp_df %>% mutate(gdp_growth = log(gdp_growth)) %>% group_by(ISO3_Code) %>% mutate(lag_gdp = dplyr::lag(gdp_growth,1)) %>%  mutate(gdp_growth = dplyr::lead(gdp_growth,.x) - gdp_growth)) %>% 
  map(~ .x %>% mutate(Currency_crisis_severe_norm = ifelse(Currency_crisis_severe_norm > 0,1,0))) %>% 
  map(~ .x %>% mutate(Currency_crisis_severe_norm = dplyr::lead(Currency_crisis_severe_norm,1))) %>% 
  map(~ .x %>% ungroup())

# Run models:

results_jorda <- list_jorda_df %>% 
  map(~ plm(gdp_growth ~ Currency_crisis_severe_norm + lag_gdp, .x, effect = "individual",model = "within")) %>% 
  map(~ data.frame(coef = .x[["coefficients"]]*100, ci = confint(.x)*100)) %>% 
  map(~ .x %>% slice(1)) %>% 
  bind_rows() %>% 
  cbind(periods) %>% 
  rename(lower = ci.2.5.., 
         upper = ci.97.5..)

# Plot IRF:

plot_jorda <- results_jorda %>% 
  ggplot(aes(periods, coef)) +
  geom_line(col = "blue") +
  geom_line(aes(y = lower), linetype = "dashed", col = "white") +
  geom_line(aes(y = upper), linetype = "dashed", col = "white") +
  geom_ribbon(aes(ymin = lower, ymax = upper),alpha = 0.2) +
  theme_bw() +
  xlab("")

list(df_results = results_jorda, plot = plot_jorda)

}


local_proj_dummy("complete")[["plot"]]

```
# Comparison 
```{r echo = F}

results <- list(local_proj_dummy("complete"), local_proj_rr("complete"))

results_df <- results %>% 
  map("df_results") %>% 
  bind_cols() %>% 
  select(-periods1)



irfs_dummy <- ggplot(results_df,aes(x = periods)) +
  geom_line(aes(y = coef, col = "Text Index - Currency Crisis"), size = 1) +
  geom_line(aes(y = coef_rr, col = "RR - Currency Crisis"), size = 1) +
  geom_line(aes(y = upper_rr, col = "RR - Currency Crisis"), linetype = "dashed") +
  geom_line(aes(y = lower_rr, col = "RR - Currency Crisis"), linetype = "dashed") +
  geom_line(aes(y = upper, col = "Text Index - Currency Crisis"), linetype = "dashed") +
  geom_line(aes(y = lower, col = "Text Index - Currency Crisis"), linetype = "dashed") +
  theme_bw() +
  xlab("") +
  ylab("") +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  scale_y_continuous(breaks = c(3:-6)) +
  coord_cartesian(ylim = c(3, -6))

output[["irfs_dummy"]] <- irfs_dummy

# Show:

irfs_dummy

```
# Local proj. with continuos index: (WIP)
```{r echo=F}

local_proj_continuos <- function(country_group){
  
  if(country_group != "complete"){
    lp_df <- lp_df %>% filter(group == country_group)
  }
  
  
  list_jorda_df <- periods %>%
    map(~ lp_df %>% mutate(gdp_growth = log(gdp_growth)) %>% mutate(lag_gdp = dplyr::lag(gdp_growth,1)) %>%      group_by(ISO3_Code) %>% mutate(gdp_growth = dplyr::lead(gdp_growth,.x) - gdp_growth)) %>% 
    map(~ .x %>% mutate(Currency_crisis_severe_norm = dplyr::lead(Currency_crisis_severe_norm,1))) %>% 
    map(~ .x %>% ungroup())
  
  # Run models:
  
  results_jorda <- list_jorda_df %>% 
    map(~ plm(gdp_growth ~ Currency_crisis_severe_norm + lag_gdp, .x, effect = "individual",model = "within")) %>% 
    map(~ data.frame(coef = .x[["coefficients"]]*100, ci = confint(.x)*100)) %>%
    map(~ .x %>% slice(1)) %>% 
    bind_rows() %>% 
    cbind(periods) %>% 
    rename(lower = ci.2.5.., 
           upper = ci.97.5..)
  
  # Plot IRF:
  
  plot_jorda <- results_jorda %>% 
    ggplot(aes(periods, coef)) +
    geom_line(col = "blue") +
    geom_line(aes(y = lower), linetype = "dashed", col = "white") +
    geom_line(aes(y = upper), linetype = "dashed", col = "white") +
    geom_ribbon(aes(ymin = lower, ymax = upper),alpha = 0.2) +
    theme_bw() +
    xlab("") +
    ylab("")
  
  list(df_results = results_jorda, plot = plot_jorda)
  
}


local_proj_continuos("complete")[["plot"]]

```



